### 2014-02-24 doc/uist14/control.tex
create folder uist14 and copy content from sigchi14

For this study, we only elicited subjective data in the form of Likert data and open-ended responses.
\begin{figure}[b]
\centering
\includegraphics[width=1.0\columnwidth]{figures/scenario-likert.pdf}
\caption{Likert scale ratings for ease of use of aspects of the smart home control scenario. Error bars show standard error.}
\label{fig:smarthome-likert}
\end{figure}

\subsection{Results}
All participants successfully completed the list of tasks.
Participants stated it was easy to interact with the appliances, but there were distinct differences between appliances. Ease of use ratings were higher for the lamp and fan which had simple, discrete on/off actions, and lower for the more complex movie player (see Figure~\ref{fig:smarthome-likert}). Multiple participants remarked that the difficulty was based on the affordances of Glass: \studyquote{Most of the difficulty I had with Glass came from having to navigate the interface on the tiny screen with the touch pad}. The screen size and 1D input put a limit on the complexity of interfaces that can be presented.

\subsubsection{Visual overlap between Near-Eye Display and Target Appliance}
When a participant looks at a target, the near-eye display may occlude or overlap the target appliance. This may make it difficult to read either the on-screen display or see information displayed on the target device.  As one participant remarked \studyquote{This was especially annoying with the TV because there were two screens overlapping each other.} While it is possible to look away once a device has been acquired to better see the Glass display, this tension is likely to remain for users who want to rely on feedback from the devices themselves instead of the Glass display.

>>>>

For this study, we only elicited subjective data in the form of Likert data and open-ended responses.
\begin{figure}[t]
\centering
\includegraphics[width=1.0\columnwidth]{figures/scenario-likert.pdf}
\caption{Likert scale ratings for ease of use of aspects of the smart home control scenario. Error bars show standard error.}
\label{fig:smarthome-likert}
\end{figure}

\subsection{Results}
All participants successfully completed the list of tasks. They commented positively on the universal remote control functionality (e.g., \studyquote{I didn't have to search for different remote controllers for different appliances}) and stated it was easy to target and connect to appliances, in line with the findings of the previous study procedure. Participants saw benefits of the device for families --- \studyquote{ It might also be useful for people who need to take care of small children that they can complete all the tasks while keeping an eye on their children at the same time}, though settings that require more movement than watching a movie at home (e.g., cooking) may be more appropriate scenarios for wearing the device.

\subsubsection{Simple and Complex Controls}
Participants rated the ease of control of particular appliances differently. Ease of use ratings were higher for the lamp and fan which had simple, discrete on/off actions, and lower for the more complex movie player (see Figure~\ref{fig:smarthome-likert}). Multiple participants remarked that the difficulty was based on the affordances of Glass: \studyquote{Most of the difficulty I had with Glass came from having to navigate the interface on the tiny screen with the touch pad}. The screen size and (largely) 1D input put a limit on the complexity of interfaces that can be presented. As one participant remarked: \studyquote{[The media player] does not seem to be more efficient than a tablet device.} The difficulty can also partly be ascribed to our interaction design, which required one finger swipes to switch between parameters and two finger gestures for adjusting parameters --- it was hard for users to exert fine control over two-finger swipes. In addition, users did not always remember these mappings as they are not yet part of a standard gesture vocabulary.

\subsubsection{Eliminating Steps}
Participants liked the efficiency of our design but also suggested further simplification by eliminating the explicit connection step, they wanted to immediately connect to any appliance that receives the infrared signal --- \studyquote{I intuitively want the screen to automatically appear when the IR detects the appliance rather than having to tap to connect.} Such a design would increase the efficiency of interaction, but at a power tradeoff, as the wireless radio will have to send and receive data each time the user looks at a device --- whether on purpose or inadvertently. We leave the study of battery life implications of interaction design choices to future work.

\subsubsection{Feedback On Screen or In The World}
We found out that the near-eye display may occlude or overlap the target appliance when a participant looks at a target. This may make it difficult to read either the on-screen display or see information displayed on the target device.  As one participant remarked \studyquote{This was especially annoying with the TV because there were two screens overlapping each other.} While it is possible to look away once a device has been acquired to better see the Glass display, a tension remains whether users should rely on feedback from the appliances themselves or on the near-eye display.
